Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2018-02-01 paper.tex
Update from Kang-Kuen and use dashed line for the Rabi flopping fit with decoherence instead

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (C) and (D) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The horizontal dashed line in the plot corresponds to the $96\%$ survival probability
    after the first image.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

We expect to enhance the ground state probability after RSC
by increasing the detuning of the Raman beams,
implementing better control of the magnetic field, and optimizing imaging.
Another improvement could be to implement grey molasses cooling to achieve
a lower starting temperature before RSC~\cite{Colzi2016}.

>>>>

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (C) and (D) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The horizontal dashed line in the plot corresponds to the $96\%$ survival probability
    after the first image.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green dashed line in (C) includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

We expect and have verified with Monte-Carlo simulation
to enhance the ground state probability after RSC
by increasing the detuning of the Raman beams and
implementing better control of the magnetic field.
Another improvement could be to implement grey molasses cooling to achieve
a lower starting temperature before RSC~\cite{Colzi2016}.
